### Question 0

*  Draw a concepts diagram that uses all the following Github terminology 
   * Include any missing keywords that will simplify the concepts diagrams 


`Push`, `Repository`, `Clone`, `Pull`, `Pull Request`, `Branch`, `Merging`, `Github Client`, `README file`, `Private or Public`

```{r}
# Add your photo here
![]https://drive.google.com/file/d/1QVyeD5KHZ37YT5uMpu5j8Tp-hE6oRS3O/view?usp=sharing
```

#### Question 1

`matrix(c(1,2,3,4,5,6) , nrow = 3)`

* Running the expression produces the following matrix

|  |  |
|---|---|
| 1 | 4 |
| 2 | 5 |
| 3 | 6 |

* How can you modify the call to `matrix()` to produce the following matrix instead?

|   | col_1 |  col_2 |
| --- |---|---|
| row_1 | 1 | 2 |
| row_2 | 3 | 4 |
| row_3 | 5 | 6 |

* Note that you need to name the columns (col_1 and col_2) and name the rows (row_1, row_2, row_3)

Hint: Use the `?` symbol to invoke the matrix documentation

```{r}
# Add your photo here
```

#### Question 1

`matrix(c(1,2,3,4,5,6) , nrow = 3)`

* Running the expression produces the following matrix

|  |  |
|---|---|
| 1 | 4 |
| 2 | 5 |
| 3 | 6 |

* How can you modify the call to `matrix()` to produce the following matrix instead?

|   | col_1 |  col_2 |
| --- |---|---|
| row_1 | 1 | 2 |
| row_2 | 3 | 4 |
| row_3 | 5 | 6 |

* Note that you need to name the columns (col_1 and col_2) and name the rows (row_1, row_2, row_3)

Hint: Use the `?` symbol to invoke the matrix documentation

```{r}
# Write your answer here
mymatrix<-matrix(c(1:6),nrow=3,ncol=2,byrow=TRUE,dimnames=list(c("row_1","row_2","row_3"),c("col_1","col_2")))
mymatrix
```

#### Question 2

* Load then sort the airquality data frame on its `Temp` and `Solar.R` columns in reverse order (largest to smallest values)
  * The function to sort a data frame is called order
* Display only the first 15 lines of your table

```{r}
# Write your answer here
data("airquality")
ordered<-airquality[order(-airquality$Temp, -airquality$Solar.R),]
head(ordered,n=15)
```

#### Question 3

* Sort the airquality data frame on its `Temp` in decreasing order and `Solar.R` in increasing order
* Display only the first 15 lines of your table

```{r}
# Write your answer here
ordered2<-airquality[order(-airquality$Temp, airquality$Solar.R),]
head(ordered2,n=15)
```

#### Question 4

* There are various ways to select a subset of observations from a data frame.

* Consult your [R Reference Card](https://cran.r-project.org/doc/contrib/Baggott-refcard-v2.pdf), see `Data Selection and Manipulation` section.
  * What operations can you use to select all observations where the temperature is 72. Give at least two different answers to this question


```{r}
# Write your answer here
#1
airquality$Temp==72
temp_72<-airquality$Temp==72
airquality[temp_72,]

#2
subset(airquality,Temp==72)
```

#### Question 6

* You may have noticed when working with the `airqulity` data that some values show as `NA`
 * `NA` stands for not available, or missing values.
* A major part of data wrangling consists of cleaning missing values by either:
  * Dropping the lines that have missing values
   * Sometimes we can drop the column with missing values if the column is made of predominantly missing values
  * Imputing the missing values, which uses educated guesses (or more complex algorithms) to fill the missing values
  
* Find and remove all rows that are missing values for the `Solar.R` or `Ozone` variables
* Save the cleaned data to a new data frame called airquality_no_na
  * How many lines have been removed?

```{r}
# Write your answer here
#Remove Solar.R N/A's
missing_Solar.R<-is.na(airquality$Solar.R)
airquality[missing_Solar.R,]
airquality[c(-5,-6,-11,-27,-96,-97,-98),]
#Remove Ozone N/A's
missing_Ozone<-is.na(airquality$Ozone)
airquality[missing_Ozone,]
airquality[c(-5,-10,-25,-26,-27,-32,-33,-34,-35,-36,-37,-39,-42,-43,-45,-46,-52,-53,-54,-55,-56,-57,-58,-59,-60,-61,-65,-72,-75,-83,-84,-102,-103,-107,-115,-119,-150),]
#Remove Both Solar.R and Ozone N/A's
airquality_no_na<-airquality[c(-5,-6,-10,-11,-25,-26,-27,-32,-33,-34,-35,-36,-42,-43,-45,-46,-52,-53,-54,-55,-56,-57,-58,-59,-60,-61,-65,-72,-75,-83,-84,-96,-97,-98,-102,-103,-107,-115,-119,-150),]

#153-113= 40 lines have been removed
```

#### Question 7
* Let's use a different strategy and impute the missing value.
  * replace the missing values for Solar.R using that month's average.
  * Example:
    * The missing value for line 6 should be replaced with the average for month 5.
    * The missing value for line 97 should be replaced with the average for month 8.

```{r}
# Write your answer here
#May Mean
solar_r_may<-subset(airquality,Month==5)$Solar.R
solar_r_may
mean(solar_r_may,na.rm=TRUE)
na_may<-subset(airquality,(solar_r_may)&(missing_Solar.R))
# Solar.R mean of may = 181

#Aug Mean
solar_r_aug<-subset(airquality,Month==8)$Solar.R
solar_r_aug
mean(solar_r_aug,na.rm=TRUE)
#Solar.R mean of aug = 172

#Replace NA's with means

airquality[5,2]=181
airquality[6,2]=181
airquality[11,2]=181
airquality[27,2]=181
airquality[96,2]=172
airquality[97,2]=172
airquality[98,2]=172
```

